GeoSPARQL 1.1: An Almost Decadal Update to the Most Important Geospatial LOD Standard

### 2021-08-20 manuscript.tex
copyright notice

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

@@

\title{GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard}
\titlerunning{GeoSPARQL 1.1}

@@

>>>>

\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\usepackage{tikz}

@@

\newcommand\copyrighttext{%
  \footnotesize Copyright ©2021 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
\newcommand\copyrightnotice{%
\begin{tikzpicture}[remember picture,overlay]
\node[anchor=south,yshift=10pt] at (current page.south) {\fbox{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\copyrighttext}}};
\end{tikzpicture}%
}

@@

\title{GeoSPARQL 1.1: An Almost Decadal Update to the Most Important Geospatial LOD Standard}
\titlerunning{GeoSPARQL 1.1}

@@

\copyrightnotice
